# ---
title: "Binomial package"
author: "Jiahao Cao"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Binomial package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
library(ggplot2)
```

## binomial

The package `"binomial"` is a minimal implements functions for
calculating probabilities of a Binomial random variable, and related calculations such as the
probability distribution


## Combination number

The first thing we can do is to calculate the $C_n^k$

```{r}
bin_choose(n = 5, k = 2)
bin_choose(5, 0)
bin_choose(5, 1:3)
```


## Binomial distribution

The we can get the distribution of a binomial random variable.

First is function `bin_probability`: calculate the probability:
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

Then `bin_distribution` can show all the distribution information:
```{r}
bin_distribution(trials = 5, prob = 0.5)
```

Further , `bin_cumulative` add cumulative distribution to above:
```{r}
bin_cumulative(trials = 5, prob = 0.5)
```

Also, `bin_variable` returns an object of class "binvar".
And you can use `print`,`summary` on it.
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
binsum1 <- summary(bin1)
binsum1
```

Last, there are some functions to do measurements.
```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```
## Print and plot

You can use the function `plot()` to graphs a barplot to display
the probability histogram of a binomial distribution object "bindis".


```{r, fig.show='hold'}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

also, use `plot.bincum()` to graph the cumulative distribution in ab object "bincum".
```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```


